### 2014-04-23 article.tex
Skeleton for Practical 2 in place, plus a nice table.

% Some useful packages.
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{graphicx}

@@

\lhead{BTTM8 - SURFACE WATER MODELLING}
\chead{}
\rhead{}
%\lfoot{}
%\cfoot{}
%\rfoot{}

@@

\newpage
\section{Results and analysis}

\subsection{Existing hydrodynamic regime}

Water velocity is maximum for this Estuary during a rising tide, and reaches a magnitude of \SI{8.2}{m/s}. The location of the maximum velocity is where the Estuary narrows to \SI{120}{m}. It is not the shallowest or narrowest part of the Estuary, but it is on a bending section and it is nearer the mouth than the narrowest part. The location of the fastest part of the Estuary for a falling tide is in the same place, as can be seen from Figures \ref{fig:global_velocities} and \ref{fig:local_velocities}.

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical1/global_vec_velocity_mag}
    \caption{Maximum velocities for rising (left) and falling (right) tides. Scale on left is in \SI{}{m/s}.}
    \label{fig:global_velocities}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical1/local_vec_velocity_mag}
    \caption{Local maximum velocities for rising (left) and falling (right) tides showing the fastest point of the river. Scale on left is in \SI{}{m/s}.}
    \label{fig:local_velocities}
\end{figure}

\subsection{Effects of dredging}

After dredging, the main change to the hydrodynamic regime is a reduced velocity in the Inlet and Berth areas. This can be seen in Figure \ref{fig:dredging_delta_vel_mag}, where the velocity magnitude at both the Inlet and Berth are substanitally reduced diring both rising and falling tides. The reduction is biggest at the Berth. Both Mid-estuary and Upstream locations show essentially no change in velocity magnitude under the dredging scenario. For all four locations, the surface water height is almost identical in both scenarios.

\begin{figure}[!h]
    \centering
    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/dredging_delta_vel_mag}
    \caption{Difference between original and dredged velocity magnitude, with surface water level shown for reference.}
    \label{fig:dredging_delta_vel_mag}
\end{figure}

There is an additional effect of dredging, the appearance of a localised area of increased velocity just upstream of the dredging. This is shown in %\ref{fig:dredging_hotspot}.

@@

talks about how bathymatric uncertainty can be used to cal model: \textcite{cea2012bathymetric}

@@

% Practical 2:

\part*{Modelling the effects of deforestation on a catchment area}

@@

\section{Methodology}
Methods

\section{Results}
Results to go here\ldots

>>>>

% Some useful packages.
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{verbatim}

@@

\lhead{BTTM8 - SURFACE WATER MODELLING - EFFECTS OF DREDGING}
\chead{}
\rhead{}
%\lfoot{}
%\cfoot{}
%\rfoot{}

@@

@@

TODO: finish off. Talks about how bathymatric uncertainty can be used to cal model: \textcite{cea2012bathymetric}

@@

% Practical 2:
\lhead{BTTM8 - SURFACE WATER MODELLING - EFFECTS OF LAND USE/CLIMATE CHANGE}
\part*{Modelling the effects of land use change and climate change on a catchment area}

@@

\section{Methodology}

\subsubsection{Land cover}

\subsubsection{Unsaturated zone}

\subsubsection{Saturated zone}

\subsubsection{Rivers}

\subsubsection{Precipitation}

\subsubsection{Run control}

As can be seen in Table \ref{tab:summary_stats}, \dots

\begin{table}[!h]
    \centering
    \begin{tabular}{l c c c}
	    & RMSE & NSE & R \\
	    \hline
	Borehole 1 & 0.1 & 0.9 & 0.8 \\
	Borehole 2 & 0.1 & 0.9 & 0.8 \\
	Borehole 3 & 0.1 & 0.9 & 0.8 \\
	Borehole 4 & 0.1 & 0.9 & 0.8 \\
	    \hline
	Karup & 0.1 & 0.9 & 0.8 \\
	Hagebro & 0.1 & 0.9 & 0.8 \\
    \end{tabular}
    \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two rivers.}
    \label{tab:summary_stats}
\end{table}

\subsection{Scenarios}

\subsubsection{Changing land use}

\subsubsection{Climate change}

\section{Results}

\subsection{Effects of land use change}

\subsection{Effects of climate change}
